\documentclass[11pt]{report}

\begin{document}
TEST THIS IDEA IN SUPERVISED LEARNING SETTING WITH AND WITHOUT GRU OR LSTM AND EVEN VANILLA RNN. Can this be used for classification and regression ? 

\section{Ideas recurrent learning}
Ideas to develop:
\begin{itemize}
	\item Bias variance induced by exponential smoothing
	\item Credit assignement
	\item Emphasis function
	\item Partial observability
\end{itemize}
\section{Bias variance induced by exponential smoothing}
In the tabular setting 1 experiment to show the bias variance trade-off. Need to think if it is ever a problem in reality.
\section{Credit assignement}
Need to think about the relationship with eligibility traces can they be combined ? 
Do we need to do credit assignement in the case of transfer ? Maybe transfer intra game ?
Do the example like in RNN paper. Random symbol for a while with one important symbol deciding the end. Can we convert this in continuous setting with function approximation ? I think our algorithm is completely tuned down version of LSTM optimized for specific case in RL. Can be useful in some cases and more data efficient. Learning to ignore a state altogether can be easier than learning to not update any gate of the hidden state. Maybe both can be useful add it in supervised learning ? 
\section{Emphasis function}
Useful for a lot of things:
\begin{itemize}
	\item Exploration
	\item Hardware limited, time discretization
	\item Model based
	\item Replay memory
	\item Interpretation
	\item Credit assignement
\end{itemize}
Maybe need to pick a couple and try them out ? Exploration and replay memory seem like the easiest to start.
\section{Experiments idea}
\begin{itemize}
	\item Add the RNN comparison in the pomdp experiment
\end{itemize}
\section{Ideas from reviewer}
\begin{itemize}
	\item Compare with RNN especially in the pomdp setting
	\item Extend theory by adding reward ? What if we restrict the set of beta, still have the problem of stochastic transition ? 
\end{itemize}
\section{Random thoughts}
\begin{itemize}
	\item Discretization of beta
	\item Model based with discrete beta
	\item Time discretization of continuous time process 
	\item Extend those idea in supervised learning regression ??
\end{itemize}

\end{document}
